Brownian Dynein Model

### 2015-07-22 latex/derivation.tex
get rid of * for multiplication

\section{Cartesian from Angular Coordinates}
$$X_{bl}$$
$$X_{ml} = X_{bl}+L_{t}*\cos(\Theta_{bl})$$
$$X_{t}  = X_{ml}+L_{s}*\cos(\Theta_{ml})$$
$$X_{mr} = X_{t} +L_{s}*\cos(\Theta_{mr}-\pi)$$
$$X_{br} = X_{mr}+L_{t}*\cos(\Theta_{br}-\pi)$$

$$Y_{bl}$$
$$Y_{ml} = Y_{bl}+L_{t}*\sin(\Theta_{bl})$$
$$Y_{t}  = Y_{ml}+L_{s}*\sin(\Theta_{ml})$$
$$Y_{mr} = Y_{t} +L_{s}*\sin(\Theta_{mr}-\pi)$$
$$Y_{br} = Y_{mr}+L_{t}*\sin(\Theta_{br}-\pi)$$

\section{Cartesian Velocities}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

\section{Cartesian Velocities (expanded)}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = L_{t}*\sin(\Theta_{bl}) * \dot{\Theta}_{bl} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \mn L_{t}*\cos(\Theta_{bl}) * \dot{\Theta}_{bl} + \mn L_{s}*\cos(\Theta_{ml}) * \dot{\Theta}_{ml} + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br}$$

@@

$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$

$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$

@@

$$
\dot{X}_{bl} + L_{t}*\sin(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - 
$$
$$
\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
$$

$$
\hspace*{-4cm} \dot{X}_{ml} + L_{s}*\sin(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
$$

$$\dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$

$$\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$

$$
\hspace*{-7cm} \dot{Y}_{bl} + \mn L_{t}*\cos(\Theta_{bl})     * \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
$$

$$
\hspace*{-4cm} \dot{Y}_{ml} + \mn L_{s}*\cos(\Theta_{ml})     * \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
$$

$$
\hspace*{-2cm} \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$\dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$

@@

$$
\hspace*{-4cm} \Big (\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
$$

$$
\hspace*{-4cm} \Big (L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
$$

$$
\hspace*{-4cm} \Big (L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$
\hspace*{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}*\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}*\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}*\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
\\

@@

$$
\dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
$$

$$
\dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$
\Big ( \dot{X}_{t } + L_{s}*\sin(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}*\sin(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
$$
$$
\Big ( \dot{Y}_{t } + \mn L_{s}*\cos(\Theta_{mr}-\pi) * \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}*\cos(\Theta_{br}-\pi) * \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
$$

>>>>

\section{Cartesian from Angular Coordinates}
$$X_{bl}$$
$$X_{ml} = X_{bl}+L_{t}\cos(\Theta_{bl})$$
$$X_{t}  = X_{ml}+L_{s}\cos(\Theta_{ml})$$
$$X_{mr} = X_{t} +L_{s}\cos(\Theta_{mr}-\pi)$$
$$X_{br} = X_{mr}+L_{t}\cos(\Theta_{br}-\pi)$$

$$Y_{bl}$$
$$Y_{ml} = Y_{bl}+L_{t}\sin(\Theta_{bl})$$
$$Y_{t}  = Y_{ml}+L_{s}\sin(\Theta_{ml})$$
$$Y_{mr} = Y_{t} +L_{s}\sin(\Theta_{mr}-\pi)$$
$$Y_{br} = Y_{mr}+L_{t}\sin(\Theta_{br}-\pi)$$

\section{Cartesian Velocities}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

\section{Cartesian Velocities (expanded)}
$$\dot{X}_{bl} = 0$$
$$\dot{X}_{ml} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl}$$
$$\dot{X}_{t } = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml}$$
$$\dot{X}_{mr} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{X}_{br} = L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

$$\dot{Y}_{bl} = 0$$                                                               
$$\dot{Y}_{ml} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl}$$
$$\dot{Y}_{t}  = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}$$
$$\dot{Y}_{mr} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr}$$
$$\dot{Y}_{br} = \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}$$

@@

$$\dot{X}_{ml} = \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml}$$
$$\dot{X}_{t} = \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt }$$
$$\dot{X}_{mr} = \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr}$$
$$\dot{X}_{br} = \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}$$

$$\dot{Y}_{ml} = \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml}$$
$$\dot{Y}_{t} = \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt }$$
$$\dot{Y}_{mr} = \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr}$$
$$\dot{Y}_{br} = \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}$$

@@

$$
\dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - 
$$
$$
\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl})
$$

$$
\hspace*{-4cm} \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{lt}(X_{t }
$$

$$\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })$$

$$\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr})$$

$$
\hspace{-7cm} \dot{Y}_{bl} + \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl})
$$

$$
\hspace{-4cm} \dot{Y}_{ml} + \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml})
$$

$$
\hspace{-2cm} \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$\dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr})$$

@@

$$
\hspace{-4cm} \Big (\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs} = \Big (\dot{Y}_{mr} - L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
$$

$$
\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr}) = \Big (\mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
$$

$$
\hspace{-4cm} \Big (L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$
\hspace{-4cm} \dot{\Theta}_{br} \Bigg(\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg ) = \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
$$

$$\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{t}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{t}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}$$
\\

@@

$$
\dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} = \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t })
$$

$$
\dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} = \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t })
$$

$$
\Big ( \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr} + 
\dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t }) =
$$
$$
\Big ( \dot{Y}_{t } + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t })
$$

$$
\hspace{-4cm} L_{s}\sin(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi) \dot{\Theta}_{mr} (Y_{mr} - Y_{t }) =
$$
$$
\hspace{-7.5cm} \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} (Y_{mr} - Y_{t }) - L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} (X_{mr} - X_{t }) + \Big ( \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big ( \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })
$$
